\textbf{A Serious Game for Aiding the Screening of Dyslexia in Children and Young Adults}

### 2014-06-24 acticle.tex
Add Initial Game Design Section

\section{Game Design}
\subsection{Screening Tasks}
\section{Evaluation}
\subsection{Method}
\subsubsection{Design}
\subsubsection{Apparatus and Materials}
\subsubsection{Participants}
\subsubsection{Procedure}
\subsection{Results}
\subsection{Discussion}
\section{Conclusions}
\subsection{Further Work}
\bibliography{references}
\bibliographystyle{IEEEtran}
\section{Appendix}
\end{document}

>>>>

\section{Game Design}
\label{sec:gamedesign}

Following the guidance provided by \cite{artOfGameDesign} the genre, theme, and mechanics of the dyslexia screening game were designed. The game was chosen to be of the casual \emph{2D Platform} genre, allowing to players to control a characters movement in the x-axis, jump, and interact with game objects. The simple nature and popularity of this genre will hopefully mean that there will be no bias towards users with a strong gaming background, with little for new users to learn.

There seems not to be a tried and tested method of deciding upon the game theme, instead the game designers creativity is tested. With this in mind the chosen theme for the screening game is:
\begin{center}
\textit{\textbf{The fantasy of being a lost robot}}
\end{center}
The user plays the game as a lost and lonely robot, attempting to escape an underground sewer. The robot must navigate across platforms  through the sewer, utilising objects and completing puzzles as they go.

\subsection{Screening Tasks}
\section{Evaluation}
\subsection{Method}
\subsubsection{Design}
\subsubsection{Apparatus and Materials}
\subsubsection{Participants}
\subsubsection{Procedure}
\subsection{Results}
\subsection{Discussion}
\section{Conclusions}
\subsection{Further Work}
\bibliography{references}
\bibliographystyle{IEEEtran}
\section{Appendix}
\end{document}
